Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-09-13 SubGenome Analysis.Rmd
Large renaming and reorganization

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(topGO)
library(readr)
library(readxl)
library(ggplot2)
library(tidyr)
library(dplyr)
library(VennDiagram)
library(gridExtra)
```

@@

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/loadData.R")
source("~/git/SubGenomes/R/cleanData.R")
source("~/git/SubGenomes/R/parseSubgenomes.R")
source("~/git/SubGenomes/R/addGOTerms.R")
source("~/git/SubGenomes/R/parseGOSlim.R")
# source("~/git/SubGenomes/R/createTopGO.R")
source("~/git/SubGenomes/R/parseExpressionData.R")

MFterms <- ls(GOMFTerm)

# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/loadData.R")
source("~/git/SubGenomes/R/cleanData.R")
source("~/git/SubGenomes/R/functions.R")
source("~/git/SubGenomes/R/do.R")

# source("~/git/SubGenomes/R/parseSubgenomes.R")
# source("~/git/SubGenomes/R/addGOTerms.R")
# source("~/git/SubGenomes/R/parseGOSlim.R")
# source("~/git/SubGenomes/R/createTopGO.R")
# source("~/git/SubGenomes/R/parseExpressionData.R")

# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\loadData.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\cleanData.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseGOSlim.R")
# # source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\createTopGO.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseExpressionData.R")

library(topGO)
library(readr)
library(readxl)
library(ggplot2)
library(tidyr)
library(dplyr)
library(VennDiagram)
library(gridExtra)

# topGO::groupGOTerms()
MFterms <- ls(GOMFTerm)
```
